Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-13 thesis/chapters/ch_chapter4.tex
proof read updates

The elemental abundances of a galaxy over time are sensitive to the nuclear physics and stellar astrophysics that determines which stars make what elements and when. The stellar abundance patters within a given galaxy also depend on the details of how those metals are released into the ISM through various forms of stellar feedback, and the hydrodynamic interactions that ultimately mix those elements into the ISM or eject them from the galaxy in galactic winds. Stellar abundance patterns in old, metal poor systems are the result of enrichment from substantially fewer sources than younger, more metal rich stellar populations. Because of this, studying abundance patterns in these environments allows us to place constraints on the yields of individual enrichment events and the nucleosynthetic sites of each element. The lowest mass dwarf galaxies in the Local Group, UFDs, offer some of the best constraints on these processes. These environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018}. and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Duggan2018,Nagasawa2018,Ojima2018}. It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way is much more uniform, averaging over the variety of complex hydrodynamics and feedback-driven turbulence interactions that may be driving much of the significant variance in stellar abundances seen at low metallicity. Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns low metallicity environments of the Milky Way \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}. Indeed the increase in scatter in the stellar abundance patters of low mass dwarf galaxies and UFDs has been attributed to inhomogeneous mixing and stochastic effects \citep[e.g.][]{Norris2010a,Simon2015,Mashonkina2017,Suda2017}. This complicates the interpretation of abundance patters in these galaxies, particularly for constraining individual enrichment events.

@@

Recent cosmological zoom simulations have attained sufficient resolution to follow the evolution of individual UFDs (or their progenitors at high redshift) and can investigate their chemical properties \citep{Jeon2017,Corlies2018,Escala2018,Christensen2018}. Additional works have conducted more direct investigations into what drives the enrichment process for individual sources using both hydrodynamics simulations \citep{PanScannapiecoScalo2013,Ritter2015,Safarzadeh2017,Hirai2015,Hirai2017,Emerick2018b,HaynesKobayashi2019} and semi-analytic models \citep{Beniamini2018,KrumholzTing2018}. In \cite{Emerick2018b} we demonstrate that elements released through AGB winds have both wider abundance distributions in the ISM and lower ejection fractions from the galaxy than elements released in supernovae. It is becoming increasingly clear that enrichment is quite inhomogeneous in low mass dwarf galaxies (refs?), and also that the behavior of metals from any one enrichment event depends on a significant number of complex interactions. In spite of this progress, there is still substantial work to be done in understanding the physical processes that drive both evolution of both the mean and width of stellar abundances in low-mass dwarf galaxies.

@@

\subsection{Mixing Experiment Setup}
\label{ch4:sec:experiment}
We restart our fiducial, full-physics simulation at two different times, 180 Myr, and 360 Myr, labeled as runs \runonenu~ and \runtwonu~ respectively. These correspond to two different times in the galaxy's SFR evolution, testing how much variance is expected in the metal mixing and ejection with the star formation rate. \runonenu~ occurs during the lull in star formation following the initial SFR peak, and \runtwonu~ occurs in an extended period of little to no ongoing star formation. We attempted to to evolve each simulation for 150 Myr, but due to computational constrains this was not always possible.\footnote{We began runs during the peak of star formation ($\sim 100$~Myr), but the computational cost increases substantially during this time. These runs were abandoned.}

@@

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{figures/ch4/AGB1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/NSNS1_enrichment_evolution_average_CGM} \\
\includegraphics[width=0.45\linewidth]{figures/ch4/SNE1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines), the galaxy's disk (black, solid), and the CGM (black, dashed) as averaged across all events at a given $E_{\rm ej}$. The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases (colored lines) sum to the black, solid line. \textbf{Need to remake these figures}}
\label{ch4:fig:ISM_CGM}
\end{figure*}

@@

However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:fig:ISM_evolution}). This trend -- that the fraction of metals contained in a given phases tends towards the mass fraction of that phase -- is true across all phases in the simulation. Therefore, we can consider that the metals for each source are well-mixed across the \textit{phases} of the ISM on timescales of $\sim$100-150~Myr. This is comparable, but less than, the dynamical timescale of the galaxy, $\sim$200~Myr. These two results suggest that the delay-time between when metals are available to enrich ongoing star formation is on order of $\sim$10~Myr across sources, and only significant for the lowest (E46, AGB-like) energy sources. Although well-mixed across phases, we emphasize that this does not imply that the abundances are the same across phases nor that the metals are spatially well-mixed across the galaxy. We investigate this second point further below.

@@

To frame this analysis, lets first examine what processes affect the metal mass fraction PDF. The mean metal mass fraction for a collection of gas is simply the total metal mass divided by the total gas mass. For a collection of gas elements, the mean metal mass fraction is defined as $Z_{\rm gas} = \frac{ \Sigma Z_{\rm i}M_{\rm gas,i}}{\Sigma M_{\rm gas,i}}$, where $M_{\rm gas,i}$ is the mass of the i$^{\rm th}$ homogeneous blob of gas, and $Z_{i}$ its metal mass fraction. A completely homogeneous ISM would have a $\delta$ function metal mass fraction PDF at the mean metal fraction, or $p(Z) = \delta(Z_{\rm gas})$. By definition, then, a homogeneous distribution will have a zero-width IQR, IDR, and mean-median difference. Non-uniform enrichment in a homogeneous medium will increase each of these quantities, while mixing in a non-uniform medium will tend to decrease each. In simple models of galactic chemical evolution, the mean gas abundance -- not the median -- is followed, even though the median is more indicative of the abundance of a ``typical" gas element. Because these two quantities provide a more immediate conceptual understanding of how metals are distributed in the ISM, we focus on characterizing the inhomogeneity of the followed metals by examining the mean-median difference. Though it is necessary for this quantity to be zero for metals to be homogeneously distributed in a medium, we do note that it is not a sufficient condition (the mean of a symmetric distribution is equal to the median). However, its evolution is easy to interpret conceptually. Enrichment increases this quantity by raising the mean metal fraction while keeping the median value fixed (or only slightly increasing), so long as the newly enriched mass is a small fraction of the total gas mass (as is almost always the case). Conversely, preferential removal of metals from a medium will lower this quantity. And finally, the mixing of metal-rich gas elements with metal-poor will gradually bring the mean and median values to parity. For our numerical experiments, enrichment in the whole ISM only occurs once and ejection from the ISM is easy to follow. This allows for a more clean interpretation of the evolution than examining either the IQR or the IDR.

@@

\subsection{Dependence on Radial Position}
\label{ch4:sec:radial position}
We place each source at regular, but arbitrary, positions in the galaxy without consideration for the local ISM conditions at injection. Sources are placed at the center of the galaxy ($r = 0$~pc) or at various radii (at cardinal positions at 300~pc, and 600~pc), all in the mid-place of the galaxy. Since the E46 events were likely to not self-interact, we additionally placed events at $r = 100$~pc and one event at each $r$ at about one scale height above the disk ($z = 50$~pc). For each \runonenu~ run, we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ as a function of radial position in the galaxy for each event in Figure~\ref{ch4:fig:radial position}. The points, error bars, and colors are the same as in Figure~\ref{ch4:fig:CGM_CNM_variance}.

@@

Across runs, there is no clear dependence on the radial position of the event and the fraction of metals ejected beyond the galaxy for any of the displayed runs at either 20~Myr or 100~Myr. There is a slight increase in the minimum fraction of metals ejected from the galaxy as a function of radius for the higher energy runs ($>10^{50}$~erg). This is perhaps not surprising for the largest radii as 600~pc is right near the very edge of the galaxy's disk. But again, the trend is weak and there is clearly still a great variance at both fixed $E_{\rm ej}$ and $r$. The fraction of metals in the ISM that are contained within the CNM (middle row) do not show any obvious trend at E46, but does seem to generally be lowest for the higher energy sources at the outskirts of the galaxy. Finally, the radial position does seem to affect the mixing behavior. Sources at the outskirts of the galaxy tend to be more inhomogeneous than sources at inner radii, especially at 20~Myr for the higher energy events, and the variation in behavior for these sources decreases substantially, particularly at 100~Myr. It is unclear what exactly drives these mixing differences. If feedback-driven turbulence is the dominate driver of ISM mixing in this dwarf galaxy -- as it likely is -- then sources near the center are more likely to be affected by more feedback events (due to a slightly higher $\Sigma_{\rm SFR}$) and mix more efficiently.

@@

We compute the average ISM properties within a 4-zone radius ($4 \times dx$~=~7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each \runonenu~ run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event. The E46 events clearly do a better job sampling the ISM density PDF, with a slight trend of decreasing $f_{\rm CGM}$ (more retained metals) with local ISM number density. This difference is even true after 100~Myr of evolution, but still with significant variation at fixed $n$. The number statistics limit a conclusive result for the higher energy events, but generally there does not appear to be an obvious trend in behavior of $f_{\rm CGM}$ as a function of $n$. This is perhaps because these energies are sufficient to heat up and dramatically reduce the density of the ISM in the injection region regardless of $n$. This is not the case for the E46 events. $f_{\rm CNM} / f_{\rm Disk}$ does not display any significant variation with $n$ at 100~Myr, but is slightly elevated at 20~Myr at higher densities. There is still a variety of behavior at fixed $n$. Finally, we note no obvious trends of the spread of the metal PDFs as a function of $n$ for all but the E46 run. Again, the local ISM densities is likely not too dynamically relevant to the higher energy events -- hence their lack of variation with $n$ -- but this is not true for E46. There is a fairly clear trend of increasing inhomogeneity in the CNM as a function of the initial $n$ in the injection region for E46, that is not present at 20~Myr, but is obvious at 100~Myr.

@@

Finally, we examine the companion run (\runtwonu) to see if the global star formation rate of the galaxy drives variation in these results. Although this does not help to directly account for the variation seen in the previous plots, this could provide insight into how SFR (in an averaged sense) affects the evolution of metals. We note that correlation with SFR is of interest not because the formation of stars by themselves, but rather the increase in feedback associated with a higher SFR (and thus a warmer / hotter ISM, greater turbulence in the ISM, and more significant outflows). We compare these two runs in Figure~\ref{ch4:fig:SFR_comparison_CGM_CNM}, showing runs from \runonenu~ in green and runs at the lower SFR, \runtwonu, in purple. $f_{\rm CGM}$ increases much more rapidly across injection energies in \runonenu. However, this value seems to be similar across runs for E49 and E51 by $\sim$50 Myr, with an additional increase again in the \runonenu~ simulations towards the end of the time. This initial spike, lull, and second increase corresponds to the period of active star formation, slightly lull, and increase in SFR experienced during the \runonenu~ simulations (see Figure~\ref{ch1:fig:sfr_mass_evolution}; the lull occurs between 40 and 80 Myr after the enrichment events, or during 220 - 260 Myr in that figure). The SFR is consistently low (or zero) throughout \runtwonu, with just a couple brief increases in SFR. Although E49 and E51 exhibit similar behavior across global differences in SFR, the difference in E46 is significant throughout the examined time period. As these sources do not contain enough energy to eject their metals from the galaxy by themselves, they are only ejected from the galaxy by being swept up in the ISM during other feedback events. The evolution of these events are therefore much more dependent upon the global galaxy properties.

The fraction of metals contained within the CNM of the ISM does not seem to depend too strongly on the SFR, unlike $f_{\rm CGM}$. It is generally true that after the initial $\sim$50 Myr of enrichment, a greater fraction of the metals in the ISM are contained in the CNM during the run with the lower SFR (\runtwonu), but this difference is not large and is only significant for the higher energy events. In addition, the mass fraction of the CNM is greater during run \runtwonu~ than in run \runonenu, so it may simply be that the long-term evolution of the fraction of metals in the CNM is more dependent upon the phase structure of the ISM -- which is regulated by stellar feedback -- than the feedback directly.

>>>>

The elemental abundances of a galaxy over time are sensitive to the nuclear physics and stellar astrophysics that determines which stars make what elements and when. The stellar abundance patterns within a given galaxy also depend on the details of how those metals are released into the ISM through various forms of stellar feedback, and the hydrodynamic interactions that ultimately mix those elements into the ISM or eject them from the galaxy in galactic winds. Stellar abundance patterns in old, metal poor systems are the result of enrichment from substantially fewer sources than younger, more metal rich stellar populations. Because of this, studying abundance patterns in these environments allows us to place constraints on the yields of individual enrichment events and the nucleosynthetic sites of each element. The lowest mass dwarf galaxies in the Local Group, UFDs, offer some of the best constraints on these processes. These environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018} and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Duggan2018,Nagasawa2018,Ojima2018}. It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way is much more uniform, averaging over the variety of complex hydrodynamics and feedback-driven turbulence interactions that may be driving much of the significant variance in stellar abundances seen at low metallicity. Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns in low metallicity environments of the Milky Way halo \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}. Indeed the increase in scatter in the stellar abundance patterns of low mass dwarf galaxies and UFDs has been attributed to inhomogeneous mixing and stochastic effects \citep[e.g.][]{Norris2010a,Simon2015,Mashonkina2017,Suda2017}. This complicates the interpretation of abundance patterns in these galaxies, particularly for constraining individual enrichment events.

@@

Recent cosmological zoom simulations have attained sufficient resolution to follow the evolution of individual UFDs (or their progenitors at high redshift) and can investigate their chemical properties \citep{Jeon2017,Corlies2018,Escala2018,Christensen2018}. Additional works have conducted more direct investigations into what drives the enrichment process for individual sources using both hydrodynamics simulations \citep{PanScannapiecoScalo2013,Ritter2015,Safarzadeh2017,Hirai2015,Hirai2017,Emerick2018b,HaynesKobayashi2019} and semi-analytic models \citep{Beniamini2018,KrumholzTing2018}. In \cite{Emerick2018b} we demonstrate that elements released through AGB winds have both wider abundance distributions in the ISM and lower ejection fractions from the galaxy than elements released in supernovae.
% It is becoming increasingly clear that enrichment is quite inhomogeneous in low mass dwarf galaxies (refs?), and also that the behavior of metals from any one enrichment event depends on a significant number of complex interactions.
In spite of this progress, there is still substantial work to be done in understanding the physical processes that drive both evolution of both the mean and width of stellar abundances in low-mass dwarf galaxies.

@@

\subsection{Mixing Experiment Setup}
\label{ch4:sec:experiment}
We restart our fiducial, full-physics simulation at two different times, 180 Myr, and 360 Myr, labeled as runs \runonenu~and \runtwonu~respectively. These correspond to two different times in the galaxy's SFR evolution, testing how much variance is expected in the metal mixing and ejection with the star formation rate. \runonenu~occurs during the lull in star formation following the initial SFR peak, and \runtwonu~occurs in an extended period of little to no ongoing star formation. We attempted to to evolve each simulation for 150 Myr, but due to computational constrains this was not always possible.\footnote{We began runs during the peak of star formation ($\sim 100$~Myr), but the computational cost increases substantially during this time. These runs were abandoned.}

@@

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{figures/ch4/AGB1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/NSNS1_enrichment_evolution_average_CGM} \\
\includegraphics[width=0.45\linewidth]{figures/ch4/SNE1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines), the galaxy's disk (black, solid), and the CGM (black, dashed) as averaged across all events at a given $E_{\rm ej}$. The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases (colored lines) sum to the black, solid line.}
\label{ch4:fig:ISM_CGM}
\end{figure*}

@@

However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:fig:ISM_evolution}). This trend -- that the fraction of metals contained in a given phase tends towards the mass fraction of that phase -- is true across all phases in the simulation. Therefore, we can consider that the metals for each source are well-mixed across the \textit{phases} of the ISM on timescales of $\sim$100-150~Myr. This is comparable, but less than, the dynamical timescale of the galaxy, $\sim$200~Myr. These two results suggest that the delay-time between when metals are available to enrich ongoing star formation is on order of $\sim$10~Myr across sources, and only significant for the lowest (E46, AGB-like) energy sources. Although well-mixed across phases, we emphasize that this does not imply that the abundances are the same across phases nor that the metals are spatially well-mixed across the galaxy. We investigate this second point further below.

@@

To frame this analysis, lets first examine what processes affect the metal mass fraction PDF. The mean metal mass fraction for a collection of gas is simply the total metal mass divided by the total gas mass. For a collection of gas elements, the mean metal mass fraction is defined as $Z_{\rm gas} = \frac{ \Sigma Z_{\rm i}M_{\rm gas,i}}{\Sigma M_{\rm gas,i}}$, where $M_{\rm gas,i}$ is the mass of the i$^{\rm th}$ homogeneous blob of gas, and $Z_{i}$ its metal mass fraction. A completely homogeneous ISM would have a $\delta$ function metal mass fraction PDF at the mean metal fraction, or $p(Z) = \delta(Z_{\rm gas})$. By definition, then, a homogeneous distribution will have a zero-width IQR, IDR, and mean-median difference. Non-uniform enrichment in a homogeneous medium will increase each of these quantities, while mixing in a non-uniform medium will tend to decrease each. In simple models of galactic chemical evolution, the mean gas abundance -- not the median -- is followed, even though the median is more indicative of the abundance of a ``typical" gas element. Because these two quantities provide a more immediate conceptual understanding of how metals are distributed in the ISM, we focus on characterizing the inhomogeneity of the followed metals by examining the mean-median difference. Though it is necessary for this quantity to be zero for metals to be homogeneously distributed in a medium, we do note that it is not a sufficient condition (the mean of a symmetric distribution is equal to the median). However, its evolution is easy to interpret conceptually. Enrichment increases this quantity by raising the mean metal fraction while keeping the median value fixed (or only slightly increasing), so long as the newly enriched mass is a small fraction of the total gas mass (as is almost always the case). Conversely, preferential removal of metals from a medium will lower this quantity. And finally, the mixing of metal-rich gas elements with metal-poor will gradually bring the mean and median values to parity. For our numerical experiments, enrichment in the whole ISM only occurs once and ejection from the ISM is easy to follow. This allows for a cleaner interpretation of the evolution than examining either the IQR or the IDR.

@@

\subsection{Dependence on Radial Position}
\label{ch4:sec:radial position}
We place each source at regular, but arbitrary, positions in the galaxy without consideration for the local ISM conditions at injection. Sources are placed at the center of the galaxy ($r = 0$~pc) or at various radii (at cardinal positions at 300~pc, and 600~pc), all in the mid-place of the galaxy. Since the E46 events were likely to not self-interact, we additionally placed events at $r = 100$~pc and one event at each $r$ at about one scale height above the disk ($z = 50$~pc). For each \runonenu~run, we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ as a function of radial position in the galaxy for each event in Figure~\ref{ch4:fig:radial position}. The points, error bars, and colors are the same as in Figure~\ref{ch4:fig:CGM_CNM_variance}.

@@

Across runs, there is no clear dependence on the radial position of the event and the fraction of metals ejected beyond the galaxy for any of the displayed runs at either 20~Myr or 100~Myr. There is a slight increase in the minimum fraction of metals ejected from the galaxy as a function of radius for the higher energy runs ($>10^{50}$~erg). This is perhaps not surprising for the largest radii as 600~pc is right near the very edge of the galaxy's disk. But again, the trend is weak and there is clearly still a great variance at both fixed $E_{\rm ej}$ and $r$. The fraction of metals in the ISM that are contained within the CNM (middle row) do not show any obvious trend at E46, but does seem to generally be lowest for the higher energy sources at the outskirts of the galaxy. Finally, the radial position does seem to affect the mixing behavior. Sources at the outskirts of the galaxy tend to be more inhomogeneous than sources at inner radii, especially at 20~Myr for the higher energy events, and the variation in behavior for these sources decreases substantially, particularly at 100~Myr. It is unclear what exactly drives these mixing differences. If feedback-driven turbulence is the dominant driver of ISM mixing in this dwarf galaxy -- as it likely is -- then sources near the center are more likely to be affected by more feedback events (due to a slightly higher $\Sigma_{\rm SFR}$) and mix more efficiently.

@@

We compute the average ISM properties within a 4-zone radius ($4 \times dx$~=~7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each \runonenu~run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event. The E46 events clearly do a better job sampling the ISM density PDF, with a slight trend of decreasing $f_{\rm CGM}$ (more retained metals) with local ISM number density. This difference is even true after 100~Myr of evolution, but still with significant variation at fixed $n$. The number statistics limit a conclusive result for the higher energy events, but generally there does not appear to be an obvious trend in behavior of $f_{\rm CGM}$ as a function of $n$. This is perhaps because these energies are sufficient to heat up and dramatically reduce the density of the ISM in the injection region regardless of $n$. This is not the case for the E46 events. $f_{\rm CNM} / f_{\rm Disk}$ does not display any significant variation with $n$ at 100~Myr, but is slightly elevated at 20~Myr at higher densities. There is still a variety of behavior at fixed $n$. Finally, we note no obvious trends of the spread of the metal PDFs as a function of $n$ for all but the E46 run. Again, the local ISM densities is likely not too dynamically relevant to the higher energy events -- hence their lack of variation with $n$ -- but this is not true for E46. There is a fairly clear trend of increasing inhomogeneity in the CNM as a function of the initial $n$ in the injection region for E46, that is not present at 20~Myr, but is obvious at 100~Myr.

@@

Finally, we examine the companion run (\runtwonu) to see if the global star formation rate of the galaxy drives variation in these results. Although this does not help to directly account for the variation seen in the previous plots, this could provide insight into how SFR (in an averaged sense) affects the evolution of metals. We note that correlation with SFR is of interest not because the formation of stars by themselves, but rather the increase in feedback associated with a higher SFR (and thus a warmer / hotter ISM, greater turbulence in the ISM, and more significant outflows). We compare these two runs in Figure~\ref{ch4:fig:SFR_comparison_CGM_CNM}, showing runs from \runonenu~in green and runs at the lower SFR, \runtwonu, in purple. $f_{\rm CGM}$ increases much more rapidly across injection energies in \runonenu. However, this value seems to be similar across runs for E49 and E51 by $\sim$50 Myr, with an additional increase again in the \runonenu~simulations towards the end of the time. This initial spike, lull, and second increase corresponds to the period of active star formation, slightly lull, and increase in SFR experienced during the \runonenu~simulations (see Figure~\ref{ch1:fig:sfr_mass_evolution}; the lull occurs between 40 and 80 Myr after the enrichment events, or during 220 - 260 Myr in that figure). The SFR is consistently low (or zero) throughout \runtwonu, with just a couple brief increases in SFR. Although E49 and E51 exhibit similar behavior across global differences in SFR, the difference in E46 is significant throughout the examined time period. As these sources do not contain enough energy to eject their metals from the galaxy by themselves, they are only ejected from the galaxy by being swept up in the ISM during other feedback events. The evolution of these events are therefore much more dependent upon the global galaxy properties.

The fraction of metals contained within the CNM of the ISM does not seem to depend too strongly on the SFR, unlike $f_{\rm CGM}$. It is generally true that after the initial $\sim$50 Myr of enrichment, a greater fraction of the metals in the ISM are contained in the CNM during the run with the lower SFR (\runtwonu), but this difference is not large and is only significant for the higher energy events. In addition, the mass fraction of the CNM is greater during run \runtwonu~than in run \runonenu, so it may simply be that the long-term evolution of the fraction of metals in the CNM is more dependent upon the phase structure of the ISM -- which is regulated by stellar feedback -- than the feedback directly.

### 2019-04-13 thesis/chapters/ch_conclusion.tex
proof read updates

In agreement with predictions from \cite{KrumholzTing2018}, we find that the abundances of the AGB-wind metals are more inhomogeneous than the abundances of metals from supernovae. This spread can be significant, over 1~dex for the AGB-wind elements. We predict then that -- at least in the low metallicity environments of low mass dwarf galaxies -- the observed stellar abundance distributions for AGB-wind elements should be characterized by markedly greater spreads than abundance distributions for SNe elements (e.g. O, Mg). Indeed, this is observed in the stellar abundance patters of dwarf galaxies in the Local Group \citep{Suda2017}, but it remains to be seen if this is a conclusive signature of these mixing differences or perhaps is due to larger differences in star-to-star metal yields for these elements. Finally, we were able to characterize the metal mass fraction PDFs for each element across each phase of the ISM, and found that each were generically well-fit by a combined log-normal PDF with a power-law tail towards higher metal mass fractions. We hope that this characterization lends itself well to developing a physically-motivated semi-analytic prescription for stellar abundance spreads to be used in semi-analytic (and one-zone) models of galactic chemical evolution.

>>>>

In agreement with predictions from \cite{KrumholzTing2018}, we find that the abundances of the AGB-wind metals are more inhomogeneous than the abundances of metals from supernovae. This spread can be significant, over 1~dex for the AGB-wind elements. We predict then that -- at least in the low metallicity environments of low mass dwarf galaxies -- the observed stellar abundance distributions for AGB-wind elements should be characterized by markedly greater spreads than abundance distributions for SNe elements (e.g. O, Mg). Indeed, this is observed in the stellar abundance patterns of dwarf galaxies in the Local Group \citep{Suda2017}, but it remains to be seen if this is a conclusive signature of these mixing differences or perhaps is due to larger differences in star-to-star metal yields for these elements. Finally, we were able to characterize the metal mass fraction PDFs for each element across each phase of the ISM, and found that each were generically well-fit by a combined log-normal PDF with a power-law tail towards higher metal mass fractions. We hope that this characterization lends itself well to developing a physically-motivated semi-analytic prescription for stellar abundance spreads to be used in semi-analytic (and one-zone) models of galactic chemical evolution.
